Customer Community Identification from Community Detection Graph in E-Commerce

### 2016-09-10 draft paper/paper_ihsan.tex
Change paper until methodology

%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Integrated Girvan-Newman and K-means Algorithm for Customer Segmentation in E-commerce}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Ihsan Satriawan}
\IEEEauthorblockA{School of Electronic Egineering and Informatics\\
Institute of Technology Bandung\\
Bandung, Indonesia\\
ihsan.satriawan.20[at]gmail.com}
\and
\IEEEauthorblockN{G.A. Putri Saptawati}
\IEEEauthorblockA{School of Electronic Egineering and Informatics\\
Institute of Technology Bandung\\
Bandung, Indonesia\\
Putri[at]informatika.org}}

@@

\begin{IEEEkeywords}
Data Mining, Clustering, Customer Segmentation, Community Detection
\end{IEEEkeywords}

@@

Dengan besarnya nilai potensi pasar online di Indonesia, tidak aneh jika begitu banyaknya perusahaan di ranah e-commerce, seperti Tokopedia, Bukalapak, Hijup, MatahariMall, dll.
Hal tersebut mengakibatkan persaingan yang terjadi begitu kompetitif, sehingga membuat perusahaan harus dapat memberikan pelayanan yang lebih baik dibandingkan yang lain. Segmentasi pelanggan merupakan salah satu cara yang dapat dilakukan oleh perusahaan dalam rangka memahami perilaku pelanggannya sehingga dapat meningkatkan pelayanan yang sudah ada.

Salah satu teknik yang dapat digunakan untuk memproses data yang dimiliki perusahaan untuk menghasilkan segmentasi pelanggan adalah data mining. Data mining merupakan teknik untuk menemukan pola dari data dan mendapatkan informasi yang berguna.

Clustering merupakan salah satu metode data mining untuk mengelompokkan objek berdasarkan karakteristik yang dimiliki. Dengan demikian clustering dapat dimanfaatkan perusahaan untuk melakukan segmentasi pelanggan, dengan melakukan pengelompokkan pelanggan berdasarkan karakteristik tertentu seperti demografi, pola pembelian, dll.

Deteksi komunitas menggunakan pendekatan graf dalam melakukan pengelompokkan pelanggan. Proses pengelompokkan pelanggan pada deteksi komunitas berdasarkan sekumpulan simpul dengan hubungan didalam kelompok yang erat dan hubungan yang jarang di antara kelompok.

Pada penelitian ini, kami sudah melakukan pendekatan lain, yakni melakukan integrasi proses deteksi komunitas dan clustering dalam menghasilkan segmentasi pelanggan. Pendekatan ini dilakukan dengan melakukan pengelompokkan pelanggan berdasarkan pola interaksi yang terjadi antar pelanggan, hal ini untuk menemukan komunitas yang terjadi di pelanggan. Pelanggan yang telah terdeteksi komunitas nya menjadi masukan proses clustering untuk menemukan segmen nya masing-masing, nilai RFM menjadi nilai dasar pembentukan segmen untuk setiap pelanggan.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command, the
% \label for the overall figure must come after \caption.
% \hfil must be used as a separator to get equal spacing.
% The subfigure.sty package works much the same way, except \subfigure is
% used instead of \subfloat.
%
%\begin{figure*}[!t]
%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
%\label{fig_second_case}}}
%\caption{Simulation results}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the 
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that IEEE does not put floats in the very first column - or typically
% anywhere on the first page for that matter. Also, in-text middle ("here")
% positioning is not used. Most IEEE journals/conferences use top floats
% exclusively. Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the \fnbelowfloat
% command of the stfloats package.

\section{Related Work}
Terdapat penelitian yang mengangkat topik segmentasi pelanggan

\section{Methodology}
\section{Experimental Result}
\section{Conclusion}
The conclusion goes here.

@@

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

>>>>

%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Customer Community Identification from Community Detection Graph in E-Commerce}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Ihsan Satriawan}
\IEEEauthorblockA{School of Electronic Engineering and Informatics\\
Institute of Technology Bandung\\
Bandung, Indonesia\\
ihsan.satriawan.20[at]gmail.com}
\and
\IEEEauthorblockN{G.A. Putri Saptawati}
\IEEEauthorblockA{School of Electronic Engineering and Informatics\\
Institute of Technology Bandung\\
Bandung, Indonesia\\
putri[at]informatika.org}}

@@

\begin{IEEEkeywords}
Community Detection, Graph, Community Identification
\end{IEEEkeywords}

@@

Based on those potential value, no wonder if Indonesia has many E-commerce companies like Tokopedia, Bukalapak, Hijup, MatahaMall, etc. This condition make every company must give better service than other and make their customer satisfied if want to survive. Company must be able to understand their customer behavior when bought product and arrange marketing strategy based on that information \cite{Tsiptsis}.

Data mining is crucial for extracting and identifying useful information from a large amount of data \cite{Ahmed}. E-Commerce company operate databases in a long way, such that all transactions are stored in chronological order. A record-of-transaction database typically contains the transaction date and the products bought in the course of a given transaction. Usually, each record also contains an customer ID, particularly when the purchase was made using a credit card or a frequentbuyer card \cite{Ahmed}.

Networks have become ubiquitous as data from many different disciplines can be naturally mapped to graph structures \cite{Malliaros}. An interesting feature that real networks present is the clustering or community structure property, under which the graph topology is organized into modules commonly called community detection. Informally, Community detection is to partition the set of network nodes into multiple groups such that the nodes within a group are connected densely, but connections between groups are sparse \cite{Malliaros}

In this research, we have use another approach to extract useful information from data e-commerce. We modelled data e-commerce as graph and apply community detection method to get customer community and extract useful information from community.

\section{Related Work}
There are some research about community detection. The Girvan-Newman (GN) algorithm proposed by Girvan and Newman \cite{Newman} exploits the concept of edge betweenness, which is a measure of the centrality and influence of an edge in a network. Community detection in weighted graph based on twitter data use GN algorithm by Mairisha \cite{Mairisha}. Based on the time complexity of some of the methods for large networks, a detection method with a small time complexity was required. The best method that was found was the detection method first proposed by Newman and Girvan \cite{Kameyama}

However, community in networks depends on what we define relation each node. We still need to identify each community. In order to perform this task, another procedure is required, a different property must be used to identify the communities. In many cases, a possible choice is to use the semantics of a community as a unique property. For example, with the TF-IDF technique apply by Uchida et al \cite{Uchida}, an attempt was made to characterize the communities detected in a blogosphere. Specific topics discussed in each community were found, and it was shown that the communities can be identified by such specific topics. Thus, it can be considered that semantics is a useful property for identifying a community

Research by Uchida et all, use TF-IDF to identify communities detected without apply feature reduction and term weighted. it's potential error in choose term to identify topic in entries/document \cite{Dai}. Feature reduction and term weighted is part of feature selection. Feature selection becomes very important, because it features the words chosen results reduction features and patterns formed determine the precision of word weighting results grouping news \cite{Dai,DaiX}

\section{Methodology}
In this research, we apply Term Frequency-Inverse Document Frequency (TF-IDF) and Term Contribution (TC) to identify customer community. The steps of the research process as shown in figure \ref{overall_methodology}

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{figure/overall_methodology}
\caption{Overall methodology}
\label{overall_methodology}
\end{figure}

\subsection{Data Preprocessing}
This step is selects related data that we acquired from e-commerce to be used in case study of discovering customer community and then pre-processes data which is an important step. Data preprocessing eliminates irrelevant data by some methods such as data integration, data transformation, and data reduction. Prepared data is shown at Table \ref{tab:sample_data_preprocessing_result}

\begin{table}[h]
\renewcommand{\arraystretch}{1.3}
\caption{Sample Data Preprocessing Result}
\label{tab:sample_data_preprocessing_result}
\centering
\begin{tabular}{c|c|c}
    \hline
    ID-Sender  &  ID-Receiver & Total Frequency Interaction\\
    \hline
    79424 & 78112 & 2\\
    \hline
    64554 & 43874 & 2\\
    \hline
    48249 & 21061 & 18\\
    \hline
\end{tabular}
\end{table}

\subsection{Graph Modeling}
We construct a network regarding customers as nodes and interaction each customers (column "Total Frequency Interaction" in Table \ref{tab:sample_data_preprocessing_result}) as undirected edges ,although interaction is directed, we consider the network undirected, making each edge bidirectional. For make each edge bidirectional, we apply symmetrizing, equation \ref{eq:symmetrizing} show that formula \cite{Gopalakrishnan}

\begin{equation}
	\label{eq:symmetrizing}
	\bar{A} = (A + A^T)/2
\end{equation}

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth, height=3cm,keepaspectratio]{figure/bidirectional_edge}
\caption{Example of a weighted directed network}
\label{bidirectional_edge}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth, height=3cm,keepaspectratio]{figure/undirected_edge}
\caption{Symmetrized version of the weighted directed network shown in Fig \ref{bidirectional_edge}}
\label{undirected_edge}
\end{figure}

\subsection{Community Detection}
The GN algorithm is a divisive hierarchical clustering algorithm exploiting the concept of edge betweenness \cite{Newman}. Three methods were proposed for the calculation of edge betweenness. Among them, the shortest-path method typically shows the best results. The edge betweenness of an edge is informally the number of shortest paths between pairs of nodes that pass through it. Since communities are loosely connected by a few “intergroup” edges, all shortest paths between different communities must pass through one of these few edges. Then, those edges connecting communities will have high edge betweenness. Thus, the communities are detected by eliminating such edges repeatedly.

To decide how much community divide in networks, measure of quality of divide in networks, which  call the modularity. The modularity is, up to a multiplicative constant, the number of edges falling within groups minus the expected number in an equivalent network with edges placed at random, equation \ref{eq:modularity_GN} show formula from modularity GN \cite{Newman}

\begin{equation}
	\label{eq:modularity_GN}
    Q = \frac{1}{2m} \Sigma_{vw} [A_{vw} - \frac{(k_{v}k_{w})}{2m}] \sigma(c_{v}c_{w})
\end{equation}

Good community detection on graph have big modularity score, otherwise poor community detection have small modularity score. Modularity score calculate on every create new community. If formed x community, than there is x modularity score. The number of communities that have the highest modularity score indicates the formation of the community in accordance with the actual reality.
\subsection{Identify Community}
Inspired from use TF-IDF to summarization document and TC and Z-score as feature reduction in domain text mining \cite{Munggaran}, we apply this concept to identify customer community. In our case, we associate term as product and document as community and customer.

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth, height=3cm,keepaspectratio]{figure/identify_community}
\caption{Flow Identify Community}
\label{bidirectional_edge}
\end{figure}

\subsubsection{Term Frequency-Inverse Document Frequency}
TF-IDF stands for "Term Frequency, Inverse Document Frequency". It is a way to score the importance of words (or "terms") in a document based on how frequently they appear across multiple documents \cite{Lan}. TF-IDF contain two value, term frequency \((tf)\) and inverse document frequency \((idf)\), where \(tf\) is number of occurence of term in document and \(idf\) is number of document containing term. Value of \(idf\) follow equation \ref{eq:idf} and equation \ref{eq:tf-idf} shown formula for calculate TF-IDF

\begin{equation}
	\label{eq:idf}
    idf(t) = \log  \frac{D}{df(t)}
\end{equation}

\begin{equation}
	\label{eq:tf-idf}
    TFxIDF(t,d) = tf(t,d) idf(t,d)
\end{equation}

\subsubsection{Term Contribution}
TC influences the value of word frequency \((tf)\) as a component score. TC score calculate from term frequency (TF) and Inverse Document Frequency (IDF) \cite{Liu}

\begin{equation}
	\label{eq:TC_score}
    TC(t) = \Sigma_{i,j \cap i \neq j} f(t,d_{i}) X f(t,d_{j})
\end{equation}

where \(f(t,d)\) represents the \(tf*idf\) weight of term in document \(d\) whereas \(i\) and \(j\) are document \(i\) document \(j\) and \(i\) not equal \(j\). \(\Sigma f(t,d)\) is sum TF-IDF from term \(t\) in document \(d\)

\subsubsection{Z-Score}
Assuming that the important words are selected based set of words that have a high score and dominant among other, it can be determined by the difference in distance between score. Z-score calculating a value of the average deviation and density of data \cite{Olga}. This can be made possible as a solution for the elimination or  word removal. This is more flexible and can be used for different datasets. The optimal parameters can be identified at a middle value (zero). Words that have a score greater than zero \((\geq 0)\) is an important word and relevant, otherwise,  the word is not an important word and irrelevant and will be removed.

\begin{equation}
	\label{eq:Z_score}
    Z = \frac{x - \bar{x}}{\sigma}
\end{equation}

\section{Experimental Result}
As described in the previous section, we will organize the experiment results follows with the step of methodology in the previous section.

By knowing the characteristics of each segment is shown in Table VII and customer segmentation result show on Table VI, the company can provide different treatment to certain customers in the segment. For example in the Loyal Customer Segment, there are some members of that segment is incorporated in the dominant community of its members incorporated herein Profit Customer Segment, so the company can provide different treatment for these customers to be able to increase transactions, thus increasing segment type, of Loyal Customer Segment into Profit Customer Segment.

\begin{table}[h]
\renewcommand{\arraystretch}{1.3}
\caption{Character Segment}
\label{tab:Character_segment}
\centering
\begin{tabular}{c|c|c|c|c}
    \hline
    Cluster & Recency & Frequency & Monetary & Description\\
    \hline
    1 & Low & Low & Low & New Customer\\
    \hline
    2 & Low & High & High & Profit Customer\\
    \hline
    3 & High & Low & Low & Churn Customer\\
    \hline
    4 & Low & Medium & Medium & Loyal Customer\\
    \hline
    5 & Medium & High & High & Profit Customer\\
    \hline
    6 & High & Low & Low & Churn Customer\\
    \hline
\end{tabular}
\end{table}

\section{Conclusion}
This research attemps to try combine community detection and clustering process applying to customer segmentation. This research take RFM model and K-Means Clustering, and use GN algorithm for community detection then the result can be identified characteristics each segment with knowledge about community each segment. It is useful for company to develope specific strategic marketing.

@@

\bibitem{Tsiptsis}
Tsiptsis, K., and Chorianopoulos, A., "Data Mining Techniques in CRM" , Wiley 2009

\bibitem{Malliaros}
Malliaros, F. D., and Vazirgiannis, M., "Clustering and community detection in directed networks: A survey". Physics Reports 2013.

\bibitem{Ahmed}
Ahmed, R. E., Shehab, M., Morsy, S., and Mekawie, N., "Performance study of classification algorithms for consumer online shopping attitudes and behavior using data mining". 2015 Fifth International Conference on Communication Systems and Network Technologies

\bibitem{Newman}
M. E. Newman and M. Girvan, "Finding and evaluating
community structure in networks," Physical Review E,
vol. 69, no. 2, p. 026113, 2004.

\bibitem{Kameyama}
Kameyama, S., Uchida, M., Shirayama, S., "A New Method for Identifying Detected Communities Based on Graph Substructure" 2007 IEEE/WIC/ACM International Conferences on Web Intelligence and Intelligent Agent Technology

\bibitem{Uchida}
M. Uchida, N. Shibata and S. Shirayama,"Identification and Visualization of Emerging Trends from Blogosphere", Proceedings of ISWSM, pp. 305-306 (2007)

\bibitem{Mairisha}
Mairisha, M., "Integration of Coupling Degree Concept for Calculating Modularity in Quality Analysis of
Community Structure Based on Weighted Graph" Master’s Program Thesis, Institut Teknologi Bandung, 2016

\bibitem{Munggaran}
Munggaran. M. Rizky., "Identification of Trending Events From News Using Modified K-means Clustering Technique and Term Contribution Technique", Master’s Program Thesis, Institut Teknologi Bandung, 2016

\bibitem{Dai}
Dai, Xiangying, och Yunlian Sun. "Event Identification within News Topics ." IEEE ,
2010: 978-1-4244-6837-9/10.

\bibitem{DaiX}
Dai, Xiang-Ying, Qing-Cai Chen, Xiao-Long Wang, och Jun Xu. "Online Topic
Detection And Tracking Of Financial News Based On Hierarchical Clustering ."
Proceeding of International Conference on Machine Learning and Cybernetics,
2010: pp. 3341-3346.

\bibitem{Gopalakrishnan}
Gopalakrishnan, K., Balakrishnan, B., and Jordan, R., "Clusters and Communities in Air Traffic Delay Networks", 2016 American Control Conference (ACC)

\bibitem{Liu}
Liu, Tao, Shengping Liu, Zheng Chen, och Wei-Ying Ma. "An Evaluation on Feature
Selection for Text Clustering." Proceedings of the Twentieth International
Conference on Machine Learning, 2003.

\bibitem{Olga}
Olga Vechtomova, Stephen Robertson, and Susan Jones, "Query expansion with long-span collocates," Information Retrieval, vol. 6, no. 2, pp. 251-273 , 2003.

\bibitem{Lan}
Lan, Man, och Chew Lim Tan. "Supervised and Traditional Term Weighting Methods for
Automatic Text Categorization ." IEEE PAMI, 2007: VOL. 10, NO. 10.
